A robust framework for variable extrusion width concentric toolpath generation

### 2019-08-02 6_validation.tex
make figures showing strategies on gMAT example

@@

\begin{align*}
b^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
b(d) &= b^-(d) +
\begin{cases}
-1 & \text{ if } b^-(d) w_\text{pref} - d > w_\text{pref} - r_\text{max} \\
1  & \text{ if }  b^-(d) w_\text{pref} - d < w_\text{pref} - r_\text{min} \\
0 & \text{ otherwise}
\end{cases}
\\
W(n,d)_i &= 
\begin{cases}
d - (n-1) w_\text{pref} &\text{ if } i = \frac12 (n-1) \\
w_\text{pref} &\text{ otherwise }
\end{cases}
%\\
%L(n,d)_i &= 
%\begin{cases}
%d / 2 & \text{ if } i = \frac12 (n-1) \\
%w_\text{pref} \left(i + \frac12 \right) & \text{ otherwise }
%\end{cases}
\end{align*}

>>>>

\begin{figure*}
\centering
\setlength{\figwidth}{0.19\textwidth}
\setlength{\figheight}{0.283\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_widths.png}
\caption{Naive}\label{TEST_naive_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_widths.png}
\caption{Single}\label{TEST_SingleBead_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_widths.png}
\caption{Constant}\label{TEST_Constant_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_widths.png}
\caption{Center}\label{TEST_Center_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_widths.png}
\caption{Distributed}\label{TEST_Distributed_accuracy}
\end{subfigure}
%\begin{subfigure}{\figwidth}\centering
%\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_accuracy.png}
%\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_widths.png}
%\caption{Inward}\label{TEST_InwardDistributed_accuracy}
%\end{subfigure}
\begin{subfigure}{.04\columnwidth}\centering
\vspace{4cm}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/widths_legend.png}
\end{subfigure}
\caption{
Visualizing the overfills and underfills and the exaggerated widths for various beading strategies.
Grey areas are covered by extruded material,
blue areas in the top images signify underfill regions,
red areas overfill,
orange areas triply extruded areas (double overfill).
The bottom visualized the bead widths at each location by exaggerating their widths.
Cold colors are narrower than the nozzle size and warm colors are wider than the nozzle size.
}
\label{visualized_accuracy}
\end{figure*}

@@

\begin{align*}
t(n) &= \frac12 w_\text{pref} \\
b^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
b(d) &= b^-(d) +
\begin{cases}
-1 & \text{ if } b^-(d) w_\text{pref} - d > w_\text{pref} - r_\text{max} \\
1  & \text{ if }  b^-(d) w_\text{pref} - d < w_\text{pref} - r_\text{min} \\
0 & \text{ otherwise}
\end{cases}
\\
W(n,d)_i &= 
\begin{cases}
d - (n-1) w_\text{pref} &\text{ if } i = \frac12 (n-1) \\
w_\text{pref} &\text{ otherwise }
\end{cases}
%\\
%L(n,d)_i &= 
%\begin{cases}
%d / 2 & \text{ if } i = \frac12 (n-1) \\
%w_\text{pref} \left(i + \frac12 \right) & \text{ otherwise }
%\end{cases}
\end{align*}
